Computer Science House Constitution

### 2024-04-08 constitution.tex
Update constitution.tex (#220)

% Formatted as term | definition
\begin{tabular}{l l}
	Technical Seminar          & \textit{Seminar relating to computing or electronics}                                     \\
	Standard Operating Session & \textit{RIT's fall and spring semesters, excluding institute breaks and final exam weeks} \\
	Total Expenditure          & \textit{funds drawn for a specific event, project, piece of equipment, or service}
\end{tabular}

@@

\asection{House Objectives}
The objectives of CSH are:
\begin{enumerate}
	\item To enhance the education experience of its members
	\item To offer students educational programming with an emphasis in computers
	\item To provide a variety of services for its members, the RIT campus, and the Rochester Community
	\item To provide a friendly and comfortable living environment in the residence halls
\end{enumerate}

@@

\subsection{Modifiying the Constitution}
\asubsection{Non-Semantic Changes}
There are two methods for non-semantic change to the Constitution.
A Maintainer may approve any proposed change that does not affect the meaning of the document.
Alternatively, the change may be presented at a House Meeting for discussion followed by an Immediate One-Half Vote with fifty percent quorum.

\asubsection{Semantic Changes}
Any semantic change to the Constitution requires the change to be proposed in writing for discussion at a House Meeting.
Any modifications made due to the discussion are added to the written proposal and the modified proposal is posted in during the week.
The final proposal is presented the following week and ballots are distributed for a Balloted Two-Thirds Vote with two-thirds quorum \ref{Balloted Vote}.
The ballots are collected for a minimum of a forty-eight hour period.
A quorum of two-thirds of Eligible Votes must cast ballots for the vote to be official.
A vote equaling or exceeding two-thirds of the number of Votes Cast is required for the change to be placed into the Constitution.
The Constitution may be overridden by an Immediate Nine-Tenths Vote with eighty-five percent quorum as described in \ref{Immediate Vote}.

@@

% fix numbers to be only text
\asubsubsection{The Evaluation Period}
The Intro Process will occur either once or twice per semester, and will last for six weeks.
The process will be initiated by the Evals Director during either the first and second week of each semester. E-Board may approve an extension to the Intro Process by an E-Board Vote.
If an Intro Process is extended, the Intro Eval shall occur at the termination of the extended process, which may be outside of the period defined in \ref{Introductory Evaluation}.
If deemed necessary by the Evals Director or by an E-Board Vote, the second Intro Process must begin within nine days of the first process ending.
If a second Intro Process is approved, the Evals Director may initiate a new Intro Packet within the first or second week of the process.

@@

\asubsubsubsection{Voting}
On a member by member basis, the Intro Eval determines if each Intro Member has successfully completed the Intro Process requirements \ref{Expectations of an Introductory Member}.
An Immediate Relative Majority Vote with two-thirds quorum is required for the Eval to be valid.
For an Active Member to be eligible to vote during the Intro Eval they must meet the requirements outlined in \ref{Expectations of Voting Members}.
Neither absentee nor proxy votes are allowed.
Intro Members may be offered any of the outcomes listed in \ref{Outcomes}

@@

% ACTIVE MEMBERSHIP EVALUATIONS
\asubsubsection{Evaluations Processes}
During the academic year, an Active Member is evaluated by the Membership Eval.
The Membership Eval is responsible for determining those individuals who will have the option to continue Active Membership in the following year.
These meetings are open only to Active Members.
All Active Members are expected to attend the these Evals meetings.
\\* \\*
At the beginning of any Eval Process listed herein, the Evals Director must read the sections of the CSH Constitution used during the respective Eval Process.
It is incumbent upon each member to provide the Evals Director with whatever information they feel is necessary to ensure an accurate evaluation.

@@

\asubsubsubsubsection{Voting}
Any Active Member who has completed all of the requirements as defined in \ref{Expectations of Active Members} at the beginning of the Membership Eval passes their Membership Eval without being voted on.
All Active Members who have not recieved an exemption from E-Board prior to the Membership Eval will be evaluated on a member by member basis by Active Members.
The Membership Eval shall hold members to the objective requirements defined in \ref{Expectations of Active Members} and determine which members may continue as an Active Member in the following academic year.
Exceptions to the requirements may be made, as attending members may choose any of the outcomes for each member, even if the member being evaluated has not completed all of their requirements.
These requirements must be completed before the Membership Eval occurs.
A Secret Immediate Relative Majority vote with two-thirds quorum is required for the evaluation to be valid.
Neither absentee nor proxy votes are allowed.

\asubsubsubsubsection{Outcomes}
Members who pass the Membership Eval have the option to participate as an Active Member in the following year.
\\* \\*
If a member fails and has never passed a Membership Eval in the past, their membership will be revoked immediately.
If the member fails, but has previously passed a Membership Eval, they will move to Alumni Membership in bad standing, as defined in \ref{Alumni Membership Selection}, at the end of the Standard Operating Session.
In either case, the member forfeits their ability to participate as an Active Member in the following year.
\\* \\*
A member may be given a conditional to complete as a means of making up for missing requirements.
A conditional may be proposed by any member present at the Eval.
If the conditional is approved by the Evals Director, it is then voted on by the attending members as described in \ref{Voting}.
Each conditional consists of a set of additional requirements a deadline for completing them.
Members who are given a conditional have their Eval decision deferred, and therefore maintain their current membership status until the conditional is resolved.
When the deadline expires, the conditional will be brought before E-Board, who will assess its completeness.
A conditional member who does not meet these additional requirements will have failed the Eval.

@@

\asubsection{Honorary Membership Expectations}
There are no expectations associated with the Honarary Membership status.

@@

\asubsubsection{Responsibilities of the Chairperson}
\begin{enumerate}
	\item To preside over E-Board and House Meetings
	\item To exercise general supervision over the operations of E-Board
	\item To exercise general supervision over regular CSH activities
	\item To act as a liaison to the academic and administrative departments at RIT
	\item To represent CSH publicly
	\item To coordinate collaboration between CSH and companies in the industry
	\item To cast tie-breaking vote in a split decision in an E-Board Vote
\end{enumerate}

@@

\asubsubsection{Responsibilities of the Public Relations Director}
\begin{enumerate}
	\item To operate CSH social media accounts intended to represent CSH as a whole
	\item To oversee the organization and execution of CSH philanthropic events
	\item To preserve and improve the public image of CSH
	\item To collaborate with other E-Board members to organize, execute, and advertise any events that are intended to be attended by persons whom have never been Active Members
	\item To oversee the preparation of CSH for open houses, tours, and special events
	\item To vote on issues presented to E-Board
\end{enumerate}

@@

\asubsubsection{Selection of the Chairperson, Evaluations Director, Social Director(s), Financial Director, House Improvements Director, History Director,  Research and Development Director(s), Public Relations Director}
\begin{enumerate}
	\item The opening of the E-Board position(s) is announced at a House Meeting and nominations for the position are taken for a minimum of a seventy-two hour period.
	      Any member may nominate any member, or pair of members where appropriate, for a directorship.
	\item The candidates will be notified of their nomination.
	      Each candidate is given a minimum of twenty-four hour period to accept or decline the nomination.
	      A list of all nominees who have accepted their nominations will be posted shortly thereafter.
	\item The date and time of candidate speeches will be announced by a member of E-Board at least five days prior to the event.
	      All Active Members are expected to attend candidate speeches in accordance with \ref{Expectations of Active Members}.
	      If a member cannot attend due to a scheduling conflict, they may provide a reason for their absence to the Evals Director, who will record the reason with the absence.
	\item Each candidate will be given an equal amount of time to present their platform of candidacy to the attending members.
	\item Ballots will then be distributed for a Balloted Vote \ref{Balloted Vote} and voting will be open for a minimum of a forty-eight hour period.
	      The Ballots will list, in random order, all of the candidates who are qualified for a given office with a means to indicate the selection of one of the candidates.
	      In addition, an area will be provided to indicate a write-in selection of a candidate.
	\item At the end of the voting period, the Chair will terminate voting.
	\item The winners are determined via the process described in \ref{Ranked Choice}.
	      A fifty-percent quorum is required for the election to be official.
	      All winners are notified of their election.
	      If the position is currently vacant, the winner immediately assumes office.
	      If not, the winner will assume office at the end of the current term, as defined in \ref{Term}.
	      Any office whose winner declines the election, or whose winner does not fulfill the requirements of the elected office, shall have their votes redistributed in the same process as a loser in \ref{Ranked Choice}.
\end{enumerate}

@@

\asubsubsection{Impeachment}
\begin{enumerate}
	\item Impeachment of any E-Board Member may be initiated by petition, in writing, consisting of a minimum number of signatures of current members equaling or exceeding one-third the number of Eligible Votes, as defined in \ref{Eligible Votes}.
	\item The impeachment petition is then presented at an E-Board Meeting.
	      The member(s) initiating the petition present their case to E-Board.
	      E-Board then questions the accused member of the allegations.
	\item An E-Board Vote is taken on the impeachment petition, with all Voting E-Board Members present except the accused member who must be absent and whose vote counts as an Abstention, to determine if the allegations stated in the petition are legitimate grounds for impeachment.
	      If the majority of E-Board votes are negative, the petition and impeachment proceedings are dismissed.
	      This vote may be overridden by an impeachment petition consisting of the grounds for impeachment and a minimum of number of signatures of current members equaling or exceeding two-thirds the number of Eligible Votes.
	\item If the majority of the E-Board votes are positive, or the negative vote was overridden, the petition is presented at the following House Meeting and the accused and accuser(s) again present their cases.
	\item Ballots will then be distributed and a Secret Ballot Vote shall be held for a minimum of a forty-eight hour period to determine whether or not the member should be removed from office.
	      Votes shall be collected and counted for a Two-Thirds Balloted Vote, as described in \ref{Balloted Vote}.
	\item A two-thirds quorum is necessary for the vote to be official.
	      If the resolution passes, the accused officer is relinquished of their position and any benefits thereof and this position is treated like any other vacated position.
	      If a quorum cannot be reached after two attempts, or the percentage of affirmative votes does not equal or exceed the minimum, impeachment proceedings are dismissed.
	      A new selection and interim duty fulfillment procedure is followed similar to that of a resignation, as described in \ref{Executive Board Resignations}.
	\item The Secretary can be impeached according to the above process, or may be dismissed by an E-Board Vote.
\end{enumerate}

@@

\asubsection{Expenditure Approval}
All CSH expenditures must be approved by the Financial Director and the director whose budget is going to be used for the expenditure.
Single expenditures may not exceed seventy-five dollars and Total Expenditures may not exceed one-hundred dollars.
\\* \\*
If the above amounts are to be exceeded, the expenditure must be approved by an Immediate One-Half Vote at a House Meeting before the funds may be appropriated.
At the Financial Director's discretion, a Spending Committee meeting may be held in order to approve any purchase exceeding one-hundred dollars, but not to exceed three-hundred dollars.
A Two-Thirds Immediate Vote with twenty-five percent quorum is required to approve the purchase.
\\*\\*
For expenditures exceeding \$300 in total funding, a spending presentation must be presented to at a House Meeting.
This presentation includes the funds required for the expenditure, inventory of required resources, and, if applicable, a timeline for completion.
\\* \\*
If an appropriate directorship cannot be determined for an expenditure, it is to be brought up for approval at House Meeting as a miscellaneous expenditure and approved by an Immediate Relative Majority vote with fifty percent quorum, regardless of the amount.
This amount is to be directly subtracted from the general CSH account.
% HOUSING
\asection{Housing}

@@

\asubsection{Batch Vote}
When a Batch Vote is called for by the Chair of the Vote, a non-empty subset of the voting docket may be amended to a single vote.
A Two-Thirds Immediate Vote is required to allow a Batch Vote to take place.
If the call for Batch Vote passes, the subset may then be voted on, otherwise the docket remains unchanged.

>>>>

% Formatted as term | definition
\begin{tabular}{l l}
	Technical Seminar          & \textit{Seminar relating to computing or electronics}                                     \\
	Standard Operating Session & \textit{RIT's fall and spring semesters, excluding institute breaks and final exam weeks} \\
	Total Expenditure          & \textit{Funds drawn for a specific event, project, piece of equipment, or service}
\end{tabular}

@@

\asection{House Objectives}
The objectives of CSH are:
\begin{enumerate}
	\item To enhance the education experience of its members
	\item To offer students educational programming with an emphasis on computers
	\item To provide a variety of services for its members, the RIT campus, and the Rochester Community
	\item To provide a friendly and comfortable living environment in the residence halls
\end{enumerate}

@@

\subsection{Modifying the Constitution}
\asubsection{Non-Semantic Changes}
There are two methods for non-semantic change to the Constitution.
A Maintainer may approve any proposed change that does not affect the meaning of the document.
Alternatively, the change may be presented at a House Meeting for discussion followed by an Immediate One-Half Vote with fifty percent quorum.

\asubsection{Semantic Changes}
Any semantic change to the Constitution requires the change to be proposed in writing for discussion at a House Meeting.
Any modifications made due to the discussion are added to the written proposal and the modified proposal is posted during the week.
The final proposal is presented the following week and ballots are distributed for a Balloted Two-Thirds Vote with two-thirds quorum \ref{Balloted Vote}.
The ballots are collected for a minimum of a forty-eight hour period.
A quorum of two-thirds of Eligible Votes must cast ballots for the vote to be official.
A vote equaling or exceeding two-thirds of the number of Votes Cast is required for the change to be placed into the Constitution.
The Constitution may be overridden by an Immediate Nine-Tenths Vote with eighty-five percent quorum as described in \ref{Immediate Vote}.

@@

% fix numbers to be only text
\asubsubsection{The Evaluation Period}
The Intro Process will occur either once or twice per semester, and will last for six weeks.
The process will be initiated by the Evals Director during either the first or second week of each semester. E-Board may approve an extension to the Intro Process by an E-Board Vote.
If an Intro Process is extended, the Intro Eval shall occur at the termination of the extended process, which may be outside of the period defined in \ref{Introductory Evaluation}.
If deemed necessary by the Evals Director or by an E-Board Vote, the second Intro Process must begin within nine days of the first process ending.
If a second Intro Process is approved, the Evals Director may initiate a new Intro Packet within the first or second week of the process.

@@

\asubsubsubsection{Voting}
On a member-by-member basis, the Intro Eval determines if each Intro Member has successfully completed the Intro Process requirements \ref{Expectations of an Introductory Member}.
An Immediate Relative Majority Vote with two-thirds quorum is required for the Eval to be valid.
For an Active Member to be eligible to vote during the Intro Eval they must meet the requirements outlined in \ref{Expectations of Voting Members}.
Neither absentee nor proxy votes are allowed.
Intro Members may be offered any of the outcomes listed in \ref{Outcomes}

@@

% ACTIVE MEMBERSHIP EVALUATIONS
\asubsubsection{Evaluations Processes}
During the academic year, an Active Member is evaluated by the Membership Eval.
The Membership Eval is responsible for determining those individuals who will have the option to continue Active Membership in the following year.
These meetings are open only to Active Members.
All Active Members are expected to attend these Evals meetings.
\\* \\*
At the beginning of any Eval Process listed herein, the Evals Director must read the sections of the CSH Constitution used during the respective Eval Process.
It is incumbent upon each member to provide the Evals Director with whatever information they feel is necessary to ensure an accurate evaluation.

@@

\asubsubsubsubsection{Voting}
Any Active Member who has completed all of the requirements as defined in \ref{Expectations of Active Members} at the beginning of the Membership Eval passes their Membership Eval without being voted on.
All Active Members who have not received an exemption from E-Board prior to the Membership Eval will be evaluated on a member-by-member basis by Active Members.
The Membership Eval shall hold members to the objective requirements defined in \ref{Expectations of Active Members} and determine which members may continue as an Active Member in the following academic year.
Exceptions to the requirements may be made, as attending members may choose any of the outcomes for each member, even if the member being evaluated has not completed all of their requirements.
These requirements must be completed before the Membership Eval occurs.
A Secret Immediate Relative Majority vote with two-thirds quorum is required for the evaluation to be valid.
Neither absentee nor proxy votes are allowed.

\asubsubsubsubsection{Outcomes}
Members who pass the Membership Eval have the option to participate as an Active Member in the following year.
\\* \\*
If a member fails and has never passed a Membership Eval in the past, their membership will be revoked immediately.
If the member fails, but has previously passed a Membership Eval, they will move to Alumni Membership in bad standing, as defined in \ref{Alumni Membership Selection}, at the end of the Standard Operating Session.
In either case, the member forfeits their ability to participate as an Active Member in the following year.
\\* \\*
A member may be given a conditional to complete as a means of making up for missing requirements.
A conditional may be proposed by any member present at the Eval.
If the conditional is approved by the Evals Director, it is then voted on by the attending members as described in \ref{Voting}.
Each conditional consists of a set of additional requirements and a deadline for completing them.
Members who are given a conditional have their Eval decision deferred, and therefore maintain their current membership status until the conditional is resolved.
When the deadline expires, the conditional will be brought before E-Board, who will assess its completeness.
A conditional member who does not meet these additional requirements will have failed the Eval.

@@

\asubsection{Honorary Membership Expectations}
There are no expectations associated with the Honorary Membership status.

@@

\asubsubsection{Responsibilities of the Chairperson}
\begin{enumerate}
	\item To preside over E-Board and House Meetings
	\item To exercise general supervision over the operations of E-Board
	\item To exercise general supervision over regular CSH activities
	\item To act as a liaison to the academic and administrative departments at RIT
	\item To represent CSH publicly
	\item To coordinate collaboration between CSH and companies in the industry
	\item To cast the tie-breaking vote in a split decision in an E-Board Vote
\end{enumerate}

@@

\asubsubsection{Responsibilities of the Public Relations Director}
\begin{enumerate}
	\item To operate CSH social media accounts intended to represent CSH as a whole
	\item To oversee the organization and execution of CSH philanthropic events
	\item To preserve and improve the public image of CSH
	\item To collaborate with other E-Board members to organize, execute, and advertise any events that are intended to be attended by persons who have never been Active Members
	\item To oversee the preparation of CSH for open houses, tours, and special events
	\item To vote on issues presented to E-Board
\end{enumerate}

@@

\asubsubsection{Selection of the Chairperson, Evaluations Director, Social Director(s), Financial Director, House Improvements Director, History Director,  Research and Development Director(s), Public Relations Director}
\begin{enumerate}
	\item The opening of the E-Board position(s) is announced at a House Meeting and nominations for the position are taken for a minimum of a seventy-two hour period.
	      Any member may nominate any member, or pair of members where appropriate, for a directorship.
	\item The candidates will be notified of their nomination.
	      Each candidate is given a minimum of a twenty-four hour period to accept or decline the nomination.
	      A list of all nominees who have accepted their nominations will be posted shortly thereafter.
	\item The date and time of candidate speeches will be announced by a member of E-Board at least five days prior to the event.
	      All Active Members are expected to attend candidate speeches in accordance with \ref{Expectations of Active Members}.
	      If a member cannot attend due to a scheduling conflict, they may provide a reason for their absence to the Evals Director, who will record the reason with the absence.
	\item Each candidate will be given an equal amount of time to present their platform of candidacy to the attending members.
	\item Ballots will then be distributed for a Balloted Vote \ref{Balloted Vote} and voting will be open for a minimum of a forty-eight hour period.
	      The Ballots will list, in random order, all of the candidates who are qualified for a given office with a means to indicate the selection of one of the candidates.
	      In addition, an area will be provided to indicate a write-in selection of a candidate.
	\item At the end of the voting period, the Chair will terminate voting.
	\item The winners are determined via the process described in \ref{Ranked Choice}.
	      A fifty-percent quorum is required for the election to be official.
	      All winners are notified of their election.
	      If the position is currently vacant, the winner immediately assumes office.
	      If not, the winner will assume office at the end of the current term, as defined in \ref{Term}.
	      Any office whose winner declines the election, or whose winner does not fulfill the requirements of the elected office, shall have their votes redistributed in the same process as a loser in \ref{Ranked Choice}.
\end{enumerate}

@@

\asubsubsection{Impeachment}
\begin{enumerate}
	\item Impeachment of any E-Board Member may be initiated by petition, in writing, consisting of a minimum number of signatures of current members equaling or exceeding one-third the number of Eligible Votes, as defined in \ref{Eligible Votes}.
	\item The impeachment petition is then presented at an E-Board Meeting.
	      The member(s) initiating the petition present their case to E-Board.
	      E-Board then questions the accused member of the allegations.
	\item An E-Board Vote is taken on the impeachment petition, with all Voting E-Board Members present except the accused member who must be absent and whose vote counts as an Abstention, to determine if the allegations stated in the petition are legitimate grounds for impeachment.
	      If the majority of E-Board votes are negative, the petition and impeachment proceedings are dismissed.
	      This vote may be overridden by an impeachment petition consisting of the grounds for impeachment and a minimum number of signatures of current members equaling or exceeding two-thirds the number of Eligible Votes.
	\item If the majority of the E-Board votes are positive, or the negative vote was overridden, the petition is presented at the following House Meeting and the accused and accuser(s) again present their cases.
	\item Ballots will then be distributed and a Secret Ballot Vote shall be held for a minimum of a forty-eight hour period to determine whether or not the member should be removed from office.
	      Votes shall be collected and counted for a Two-Thirds Balloted Vote, as described in \ref{Balloted Vote}.
	\item A two-thirds quorum is necessary for the vote to be official.
	      If the resolution passes, the accused officer is relinquished of their position and any benefits thereof and this position is treated like any other vacated position.
	      If a quorum cannot be reached after two attempts, or the percentage of affirmative votes does not equal or exceed the minimum, impeachment proceedings are dismissed.
	      A new selection and interim duty fulfillment procedure is followed similar to that of a resignation, as described in \ref{Executive Board Resignations}.
	\item The Secretary can be impeached according to the above process, or may be dismissed by an E-Board Vote.
\end{enumerate}

@@

\asubsection{Expenditure Approval}
All CSH expenditures must be approved by the Financial Director and the director whose budget is going to be used for the expenditure.
Single expenditures may not exceed seventy-five dollars and Total Expenditures may not exceed one-hundred dollars.
\\* \\*
If the above amounts are to be exceeded, the expenditure must be approved by an Immediate One-Half Vote at a House Meeting before the funds may be appropriated.
At the Financial Director's discretion, a Spending Committee meeting may be held in order to approve any purchase exceeding one-hundred dollars, but not to exceed three-hundred dollars.
A Two-Thirds Immediate Vote with twenty-five percent quorum is required to approve the purchase.
\\*\\*
For expenditures exceeding \$300 in total funding, a spending presentation must be presented at a House Meeting.
This presentation includes the funds required for the expenditure, inventory of required resources, and, if applicable, a timeline for completion.
\\* \\*
If an appropriate directorship cannot be determined for an expenditure, it is to be brought up for approval at a House Meeting as a miscellaneous expenditure and approved by an Immediate Relative Majority vote with fifty percent quorum, regardless of the amount.
This amount is to be directly subtracted from the general CSH account.
% HOUSING
\asection{Housing}

@@

\asubsection{Batch Vote}
When a Batch Vote is called for by the Chair of the Vote, a non-empty subset of the voting docket may be amended to a single vote.
A Two-Thirds Immediate Vote is required to allow a Batch Vote to take place.
If the call for Batch Vote passes, the subset may then be voted on; otherwise, the docket remains unchanged.
